---
title: "disaggMRC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{disaggMRC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "80%", 
  fig.fullwidth = TRUE, 
  fig.width = 7,
  fig.height = 5,
  fig.align = 'center',
  dpi = 200
)
```

```{r setup}
library(disaggMRC)
```

A precipitation time series with 10 minute resolution in order to apply examples. 
```{r}
head(data_test_MRC)
```

* DJF = December, January, February,
* MAM = March, April, May, 
* JJA = June, July, Autumn,
* SON = September, October, November. 

## Parameter estimation
Estimate scaling parameters of Model A. MRC parameters are assumed to be dependent on precipitation intensity and temporal aggregation level. It returns a data frame with estimated for each season.

Parameters of Model A+ are also returned.
```{r, eval = F}
Model_A = get_scaling_params_Intensity_aggLevel(vecPrecip = data_test_MRC$obs,
                                                vecDates = data_test_MRC$date)

# parameters 
Model_A$params
```
The function `get_scaling_params_Intensity_aggLevel` returns also a list of ggplot plots. Each ggplot shows the scaling models as fitted on MRC parameters.
```{r, eval = F}
# Px 
Model_A$fig_plots$Px_aggLevel_intensity
# Scaled alpha
Model_A$fig_plots$Alpha_star_aggLevel_intensity
```
Estimate scaling parameters of Model B. MRC parameters are assumed to be dependent on precipitation intensity. It returns a data frame with estimated for each season.
```{r, eval = F}
Model_B = get_scaling_params_Intensity(vecPrecip = data_test_MRC$obs,
                                       vecDates = data_test_MRC$date)
# scaling parameters
Model_B$params
```
Fits of Model B
```{r,eval = F}
# Px 
Model_B$fig_plots$Px_intensity
# Alpha
Model_B$fig_plots$Alpha_intensity
```

## Disaggregation

Obtain a coarse resolution time series that will be used as target time series to be disaggrgeated. 
```{r, eval = F}
# a vector of dates, a date per day 
vecDates_target = unique(as.Date(data_test_MRC$date))
# get 1280 min indices 
indices_1280min = get_indices_center_1280(length(vecDates_target))
# from 10 minutes time series to "daily - 1280 min" accumulated time series 
vecPrecip_target = sum_fixed_window(x = data_test_MRC$obs[indices_1280min],
                                    k = 128)
```

Disaggregate following Model A
```{r, eval = F}
Moldel_A_disagg = disaggregate_precip_MRC_Intensity_aggLevel(vecPrecip_target = vecPrecip_target,
                                                             vecDates_target = vecDates_target,
                                                             params_scaling = Model_A$params,
                                                             res_coarse_aggLevel = 1280,
                                                             res_fine_aggLevel = 40,
                                                             nb_scenarios = 10,
                                                             asymmetry_option = F)
head(Moldel_A_disagg)
```

Disaggregate following Model B+
```{r, eval = F}
Moldel_A_disagg_asymm = disaggregate_precip_MRC_Intensity_aggLevel(vecPrecip_target = vecPrecip_target,
                                                             vecDates_target = vecDates_target,
                                                             params_scaling = Model_A$params,
                                                             res_coarse_aggLevel = 1280,
                                                             res_fine_aggLevel = 40,
                                                             nb_scenarios = 10,
                                                             asymmetry_option = T)
```


Disaggregate following Model B
```{r, eval = F}
Moldel_B_disagg = disaggregate_precip_MRC_Intensity(vecPrecip_target = vecPrecip_target,
                                                    vecDates_target = vecDates_target,
                                                    params_scaling = Model_B$params,
                                                    res_coarse_aggLevel = 1280,
                                                    res_fine_aggLevel = 40,
                                                    nb_scenarios = 10,
                                                    asymmetry_option = F)
```